### 2024-02-18 documentation/thesis/thesis_document.tex
.

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary.

In response to this, there is a growing interest in developing low-field
\gls{mri} systems that utilize in many cases permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While typically calculated images have lower resolution due to
lower magnetic field strength, low-field systems facilitate the
comparison of different field behaviours and the identification of all
kinds of irritations. O'Reilly and Teeuwisse and de Gans
\customcite{OTW19} have already demonstrated low-cost and small-scale
implementations with low-field \gls{mri} in 2021 calculating images of a
head successfully.

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring. In this generated model eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}.

The homogeneity in this configuration depends, among other things, on
the following main aspects:

@@

The focus of the ongoing efforts is to improve the homogeneity of
magnets within low-field \gls{mri}systems below \emph{1000 \gls{ppm}},
primarily driven by the goal of establishing a compact low-field
\gls{mri} for breast cancer detection.

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field \gls{mri}system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging AI-based methodologies.

@@

It is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterisation process.

To achieve this, a versatile hardware setup is in development, designed
to accommodate various sensors for the measurement of magnets or other
objects. Simultaneously, a software interface is being crafted to
universally read data from different sensors and interact seamlessly
with the diverse firmware associated with various Halbach sensors. A key
feature of this system is the ease of sensor interchangeability,
facilitating adaptability and versatility in the characterisation
process.

@@

This means that to measure a deviation of better than
\emph{1000}\gls{ppm} in a \(50mT\) magnetic field, a resolution of less
than \emph{50} \(\mu\)T is needed.

@@

The use of analogue sensors is purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They are excluded because they require more carefully designed circuits
and more complicated energy management.

In the context of the desired goal of developing a cost-efficient and
universally expandable Hall sensor interface, the decision in favour of
digital sensors seems appropriate.

@@

All parts are produced using 3D printing additive manufacturing process.
The sensor circuit board is glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised.

The exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user after connecting. The figure
\ref{Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
\caption{Result of an executed b field query using the sensors \gls{cli}
with immediate user readable response
\label{Result_of_an_executed_b_field_query_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
\end{figure}

The other option is to use the \gls{mrp}-library explained in chapter
\ref{software-readout-framework}. The serial interface is also used at
this point. However, after a connection attempt by the \gls{hal} module
(explained in chapter \ref{mrphal}) of the \gls{mrp}-library (explained
in chapter \ref{software-readout-framework}), the system switches to
binary mode, which is initiated using the \emph{sbm} command. The
command is only sent by the library, not by the user. The same commands
are available as for \gls{cli}-based communication, but in a binary
format.

@@

The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port.

To enable the most stable possible synchronisation between several
sensors, an option has already been created to establish an electrical
connection between sensors. This is used together with the firmware to
synchronise the readout intervals. The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build hardware sensors with equipped with different sensor
\gls{ic}s to cover different magnet charaterisation setups
\label{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

The table
\ref{Build_hardware_sensors_with_equipped_with_different_sensor_(+ic)s_to_cover_different_magnet_charaterisation_setups.csv}
shows the various prototype sensor platforms equipped with different
magnetic field sensors. These cover all the required functions described
in the use cases \ref{use-cases}. The most significant difference, apart
from the sensor used, is the \emph{scan mode}. In this context, this
describes whether the sensor can measure a \emph{static} fixed point on
the magnet or if the sensor can move \emph{dynamically} around the
magnet using a controllable manipulator.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}
\caption{Manufactured 1D sensor construction from different angles and
universal magnet mount (green 3D printed part) populated with N45
12x12x12mm magnet
\label{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}}
\end{figure}

The 1D sensor shown in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png}
is the simplest possible sensor that is compatible with the Unified
Sensor firmware.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6uT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers (see green part
in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_populated_with_N45_12x12x12mm_magnet.png})over
the sensor to increase the distance between the magnet and the sensor
and thus also measure these magnets.

The designed magnet holder can be adapted for different magnet shapes
and can be placed on the spacer without backlash to be able to perform a
repeatable measurement without introducing measurement irregularities by
mechanically changing the magnet.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
\caption{Full-sphere sensor implementation using two Nema17 stepper
motors in a polar coordinate system
\label{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
\end{figure}

The 3D full sphere sensor shown in figure
\ref{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
offers the possibility to create a 3D map of the inserted magnet.

The figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
\caption{3D plot of an N45 12x12x12mm magnet using the build 3D
full-sphere sensor with visible magnetic field strength deviations using
different shaded vertices on a sphere
\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full-sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}}
\end{figure}

As the magnets in the motors, as with the screws used in the 1D sensor,
can influence the measurements of the magnetic field sensor, the
distance between these components and the sensor or magnets is
increased. The turntable and its drive motor are connected to each other
via a belt.

@@

For this purpose, the library is divided into individual modules, which
are shown in the figure
\ref{MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}.
In combination, these represent a typical
measurement-analysis-evaluation workflow of data. For this purpose, a
module system with standardised functional patterns and data types is
developed and packed together in an extendable Python library.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}
\caption{MRP library implemented modules high level overview each of
which can be replaced by the user with custom ones
\label{MRP_library_implemented_modules_high_level_overview_each_of_which_can_be_replaced_by_the_user_with_custom_ones.png}}
\end{figure}

@@

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a plain text
editor. This eliminates all binary-based formats such as the
\href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
package.

Taking these points into account, the \gls{json} format is chosen. This
is human and machine readable and there is a compatible parser for every
programming language.

The following listing \ref{lst:json_export_format_example} shows an
example \gls{json} structure which is generated when a measurement that
using the library is dumped to the filesystem. By using the \gls{json}
format, all measurement points and metadata are available in readable
plain text.

This means that they can also be read out in other programs. Using
serialization, the \emph{MRPReading} class inherited from
Python-\emph{Object} class is serialized via a dictionary conversion
step. This \gls{json} string can then be processed directly or written
to the file system as a file.

@@

In addition, further custom objects can be inserted into the \gls{json}
using the functions provided.

Since there are popular data processing frameworks such as \emph{Numpy}
\customcite{HMW20}, or the program for mathematical calculations,
\emph{MATLAB} are often used, the library also supports export formats
for these systems.

The different formats can be triggered by the user by calling up the
corresponding \emph{MRPReading} class functions:

@@

\begin{itemize}
\tightlist
\item
  \emph{std\_deviation} - Standard deviation
\item
  \emph{mean} - Mean value
\item
  \emph{variance} - Variance
\item
  \emph{CoG} - Centre of gravity
\item
  \emph{binning} - Distribution of a sample by means of a histogram
\item
  \emph{k-nearest} - K-nearest neighbours
\end{itemize}

@@

The \emph{MRPProxy} module in figure
\ref{MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}
has been developed to allow forwarding and interaction with several
sensors over a network connection using a \gls{rest} interface.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}
\caption{MRPlib proxy module usage example with host \gls{pc} for
readout processing and remote \gls{pc} for sensor communication
communicating together using the http protocol
\label{MRPlib_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_communicating_together_using_the_http_protocol.png}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
\caption{Example MRP proxy module usage, using two remote \gls{pc}s
\label{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}}
\end{figure}

Figure \ref{Example_MRP_proxy_module_usage,_using_two_remote_(+pc)s.png}
shows the modified \emph{multi-proxy - multi-sensor} topology. Both
proxy instances do not communicate directly with the \emph{control}
\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
access the proxy running on \emph{remote} \gls{pc} \emph{\#1}.

@@

Figure \ref{MRPlib_Proxy_Module.png} shows the separation of the various
\gls{hal} instances, which communicate with the physically connected
sensors on the \emph{remote} \gls{pc} and the \emph{control} \gls{pc}
side, which communicates with the remote side via the network. For the
user, nothing changes in the procedure for setting up a measurement. The
\emph{MRPProxy} \gls{cli} application must always be started like shown
in listing \ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected
hardware sensors attached.

\begin{lstlisting}[language=bash, caption={MRPproxy usage to enable local sensor forwarding over the network. The (+cli) output shows the available sensor to the connected (+host) pc}, label=lst:mrpcli_proxy_start]
# START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
$ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
Proxy started. http://remotepc.local:5556/
PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
Terminate Proxy instance [y/N] [n]: 
\end{lstlisting}

After the proxy instance has been successfully started, it is optionally
possible to check the status via the \gls{rest} interface, which is
shown in listing \ref{lst:mrpcli_config_rest}:

\begin{lstlisting}[language=bash, caption={MRPProxy provided (+rest) endpoint query example using wget command line tool to send requests}, label=lst:mrpcli_config_rest]
# GET PROXY STATUS
$ wget http://proxyinstance.local:5556/proxy/status
{
"capabilities":[
  "static",
  "axis_b",
  "axis_x",
  "axis_y",
  "axis_z",
  "axis_temp",
  "axis_stimestamp"
],
"commands":[
  "status",
  "initialize",
  "disconnect",
  "combinedsensorcnt",
  "sensorcnt",
  "readsensor",
  "temp"
]}
# RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
$ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
{
"output":[
  "2"
]}
\end{lstlisting}

@@

\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a MRPproxy based network sensor}, label=lst:mrpcli_config_using_rpc]
# CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
$ MRPcli config setupsensor testcfg --path http://proxyinstance.local:5556
> remote sensor connected: True using proxy connection:
> http://proxyinstance.local:5556 with 1 local sensor connected
\end{lstlisting}

@@

As it is possible to connect many identical sensors to one host,
therefore it needs to be possible to address them separately. This
separation is done by the \emph{MRPProxy} module, which is a separate
part from the core \gls{mrp}-library, to keep installation package
dependencies small.

Each connected sensor is accessed via the text-based \gls{cli}, which is
initially the same for each sensor. The only identification feature is
the sensor \gls{uuid} by using the \emph{id} command of the sensor
\gls{cli}.

The \emph{MRPProxy} instance claims to be a sensor to the host \gls{pc}
running \gls{mrp} \gls{cli}, so multiple sensors must be combined into
one virtual one. This is done in several steps, start procedure
described by the following sub-chapters.

@@

Finally, the measurement is exported for archiving and further
processing; various export formats are available. Using the
\emph{dump\_to\_file} function, the measurement can be converted into an
open \gls{json} format.

>>>>

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary. In response to this, there
is a growing interest in developing low-field \gls{mri} systems that
utilize in many cases permanent magnets. These systems, while offering
advantages in energy efficiency and reduced complexity, face a
significant challenge related to the inherent variability in the
strength of permanent magnets. Achieving homogeneity in the magnetic
field is crucial for accurate imaging or comparative analyses. While
typically calculated images have lower resolution due to lower magnetic
field strength, low-field systems facilitate the comparison of different
field behaviours and the identification of all kinds of irritations.
O'Reilly and Teeuwisse and de Gans \customcite{OTW19} have already
demonstrated low-cost and small-scale implementations with low-field
\gls{mri} in 2021 calculating images of a head successfully.

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring. In this generated model eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}. The homogeneity in this
configuration depends, among other things, on the following main
aspects:

@@

The focus of the ongoing efforts is to improve the homogeneity of
magnets within low-field \gls{mri} systems below \emph{1000 \gls{ppm}},
primarily driven by the goal of establishing a compact low-field
\gls{mri} for breast cancer detection.

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field \gls{mri} system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging AI-based methodologies.

@@

It is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterisation process. To achieve this, a versatile hardware setup is
in development, designed to accommodate various sensors for the
measurement of magnets or other objects. Simultaneously, a software
interface is being crafted to universally read data from different
sensors and interact seamlessly with the diverse firmware associated
with various Halbach sensors. A key feature of this system is the ease
of sensor interchangeability, facilitating adaptability and versatility
in the characterisation process.

@@

This means that to measure a deviation of better than \emph{1000
\gls{ppm}} in a \(50mT\) magnetic field, a resolution of less than
\emph{50} \(\mu\)T is needed.

@@

The use of analogue sensors is purposefully avoided, though they are
suitable for more precise measurements and extended measuring ranges.
They are excluded because they require more carefully designed circuits
and more complicated energy management. In the context of the desired
goal of developing a cost-efficient and universally expandable Hall
sensor interface, the decision in favour of digital sensors seems
appropriate.

@@

All parts are produced using 3D printing additive manufacturing process.
The sensor circuit board is glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised. The exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspeaction whether
the hardware is working properly after firmware installation. The
command \emph{help}, displays a detailed command reference wit all
available commands as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user. The figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
\caption{Result of an executed b value measurement readout command using
the sensors \gls{cli} with immediate user readable response
\label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
\end{figure}

The other option is to use the \gls{mrp}-library explained in chapter
\ref{software-readout-framework}. The serial interface is also used at
this point. However, after a connection attempt by the \gls{hal} module
(explained in chapter \ref{mrphal}) of the \gls{mrp}-library (explained
in chapter \ref{software-readout-framework}), the system switches to
binary mode, which is initiated using the \emph{sbm} command. The
command is only sent by the library, not by the user. The same commands
are available to \gls{mrp}-library as for user \gls{cli}-based
communication, but in a binary format.

@@

The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. \newpage To enable the most stable
possible synchronisation between several sensors, an option has already
been created to establish an electrical connection between sensors. This
is used together with the firmware to synchronise the readout intervals.
The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build hardware sensors equipped with different sensor \gls{ic}s
to cover various magnet charaterisation setups
\label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

The table
\ref{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}
shows the various prototype sensor platforms equipped with different
magnetic field sensors. These cover all the required functions described
in the use cases \ref{use-cases}. The most significant difference, apart
from the sensor used, is the \emph{scan mode}. In this context, this
describes whether the sensor can measure a \emph{static} fixed point on
the magnet or if the sensor can move \emph{dynamically} around the
magnet using a controllable manipulator.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}
\caption{Manufactured 1D sensor construction from different angles and
universal magnet mount (green 3D printed part) equipped with N45
12x12x12mm magnet
\label{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}}
\end{figure}

The 1D sensor shown in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png}
is the simplest possible sensor that is compatible with the Unified
Sensor firmware.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6uT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers (see green part
in figure
\ref{Manufactured_1D_sensor_construction_from_different_angles_and_universal_magnet_mount_(green_3D_printed_part)_equipped_with_N45_12x12x12mm_magnet.png})over
the sensor to increase the distance between the magnet and the sensor
and thus also measure these magnets. The designed magnet holder can be
adapted for different magnet shapes and can be placed on the spacer
without backlash to be able to perform a repeatable measurement without
introducing measurement irregularities by mechanically changing the
magnet.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
\caption{Full sphere sensor implementation using two Nema17 stepper
motors in a polar coordinate system
\label{Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
\end{figure}

The 3D full sphere sensor shown in figure
\ref{Full_sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
offers the possibility to create a 3D map of the inserted magnet.

The figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
\caption{3D plot of an N45 12x12x12mm magnet using the build 3D full
sphere sensor with visible magnetic field strength deviations using
different shaded vertices on a sphere
\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}}
\end{figure}

As the magnets in the motors, as with the screws used in the 1D sensor,
can influence the measurements of the magnetic field sensor, the
distance between these and the sensor and magnet is increased by using
nylon and 3D printed spacer. The turntable and its drive motor are
connected to each other via a belt.

@@

For this purpose, the library is divided into individual modules, which
are shown in the figure
\ref{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}.
In combination, these represent a typical
measurement-analysis-evaluation workflow of data. For this purpose, a
module system with standardised functional patterns and data types is
developed and packed together in an extendable Python library.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}
\caption{A high level overview of all MRP library implemented Python
modules which can be changed by the user
\label{A_high_level_overview_of_all_MRP_library_implemented_Python_modules_which_can_be_changed_by_the_user.png}}
\end{figure}

@@

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a plain text
editor. This eliminates all binary-based formats such as the
\href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
package. Taking these points into account, the \gls{json} format is
chosen. This is human and machine readable and there is a compatible
parser for every programming language.

The following listing \ref{lst:json_export_format_example} shows an
example \gls{json} structure which is generated when a measurement that
using the library is dumped to the filesystem. By using the \gls{json}
format, all measurement points and metadata are available in readable
plain text. This means that they can also be read out in other programs.
Using serialization, the \emph{MRPReading} class inherited from
Python-\emph{Object} class is serialized via a dictionary conversion
step. This \gls{json} string can then be processed directly or written
to the file system as a file.

@@

In addition, further custom objects can be inserted into the \gls{json}
using the functions provided. Since there are popular data processing
frameworks such as \emph{Numpy} \customcite{HMW20}, or the program for
mathematical calculations, \emph{MATLAB} are often used, the library
also supports export formats for these systems. The different formats
can be triggered by the user by calling up the corresponding
\emph{MRPReading} class functions:

@@

\begin{itemize}
\tightlist
\item
  \emph{std\_deviation} - \gls{sd}
\item
  \emph{mean} - Mean value
\item
  \emph{variance} - Variance
\item
  \emph{CoG} - Centre of gravity
\item
  \emph{binning} - Distribution of a sample by means of a histogram
\item
  \emph{k-nearest} - K-nearest neighbours
\end{itemize}

@@

The \emph{MRPProxy} module in figure
\ref{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
has been developed to allow forwarding and interaction with several
sensors over a network connection using a \gls{rest} interface.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}
\caption{MRP library proxy module usage example with host \gls{pc} for
readout processing and remote \gls{pc} for sensor communication using
the http protocol
\label{MRP_library_proxy_module_usage_example_with_host_(+pc)_for_readout_processing_and_remote_(+pc)_for_sensor_communication_using_the_http_protocol.png}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
\caption{Example MRP proxy module usage using two remote \gls{pc}s
\label{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}}
\end{figure}

Figure \ref{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
shows the modified \emph{multi-proxy - multi-sensor} topology. Both
proxy instances do not communicate directly with the \emph{control}
\gls{pc}, but the proxy instance \emph{remote} \gls{pc} \emph{\#2} can
access the proxy running on \emph{remote} \gls{pc} \emph{\#1}.

@@

Figure \ref{Example_MRP_proxy_module_usage_using_two_remote_(+pc)s.png}
shows the separation of the various \gls{hal} instances, which
communicate with the physically connected sensors on the \emph{remote}
\gls{pc} and the \emph{control} \gls{pc} side, which communicates with
the remote side via the network. For the user, nothing changes in the
procedure for setting up a measurement. The \emph{MRPProxy} \gls{cli}
application must always be started like shown in listing
\ref{lst:mrpcli_proxy_start} on the \gls{pc} with connected hardware
sensors attached.

\begin{lstlisting}[language=bash, caption={MRPProxy usage to enable local sensor forwarding over the network. The CLI output shows the available sensor to the connected host PC}, label=lst:mrpcli_proxy_start]
# START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
$ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
Proxy started. http://remotepc.local:5556/
PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
Terminate Proxy instance [y/N] [n]: 
\end{lstlisting}

After the proxy instance has been successfully started, it is optionally
possible to check the status via the \gls{rest} interface, which is
shown in listing \ref{lst:mrpcli_config_rest}.

\begin{lstlisting}[language=bash, caption={MRPProxy provided REST endpoint query example using wget command line tool to send requests}, label=lst:mrpcli_config_rest]
# GET PROXY STATUS
$ wget http://proxyinstance.local:5556/proxy/status
{
"capabilities":[
  "static",
  "axis_b",
  "axis_x",
  "axis_y",
  "axis_z",
  "axis_temp",
  "axis_stimestamp"
],
"commands":[
  "status",
  "initialize",
  "disconnect",
  "combinedsensorcnt",
  "sensorcnt",
  "readsensor",
  "temp"
]}
# RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
$ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
{
"output":[
  "2"
]}
\end{lstlisting}

@@

\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a MRPProxy based network sensor}, label=lst:mrpcli_config_using_rpc]
# CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
$ MRPCli config setupsensor testcfg --path http://proxyinstance.local:5556
> remote sensor connected: True using proxy connection:
> http://proxyinstance.local:5556 with 1 local sensor connected
\end{lstlisting}

@@

As it is possible to connect many identical sensors to one host,
therefore it needs to be possible to address them separately. This
separation is done by the \emph{MRPProxy} module, which is a separate
part from the core \gls{mrp}-library, to keep installation package
dependencies small. Each connected sensor is accessed via the text-based
\gls{cli}, which is initially the same for each sensor. The only
identification feature is the sensor \gls{uuid} by using the \emph{id}
command of the sensor \gls{cli}. The \emph{MRPProxy} instance claims to
be a sensor to the host \gls{pc} running \gls{mrp} \gls{cli}, so
multiple sensors must be combined into one virtual one. This is done in
several steps, start procedure described by the following sub-chapters.

@@
